%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


\renewcommand{\baselinestretch}{1.3} 
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Data Pipeline Architect} % Job title
    {Salesforce - Autonomous Infrastructure Control Plane, AI Research} % Organization
    {Palo Alto, CA} % Location
    {May 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed real-time ETL pipelines leveraging Apache Kafka and Spark, processing 10M+ daily events into AWS Redshift data lake with automated data quality validation.}
        \item {Architected and developed entity-based compute sharding solution across 300K nodes, enabling intelligent signal preprocessing and selective data ingestion, resulting in 10x performance gains and 85\% compute cost reduction.}
        \item {Partnered with senior researchers to architect and develop ML-powered MVPs and demos, advancing model training pipelines and reinforcement learning agents for autonomous infrastructure management.}
\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Owner} % Job title
    {Salesforce - Autonomous Infrastructure Control Plane} % Organization
    {San Francisco, CA} % Location
    {Feb. 2023 - Present} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Served as distributed systems/infrastructure SME for Fortune 500 partners including Redhat, Google, and FedEx, optimizing their adoption of Salesforce's 1P infrastructure.}
      \item {Led technical architecture and product strategy, aligning cross-functional stakeholders from engineering to senior leadership to deliver cohesive product vision and roadmap.}
      \item {Managed 8+ engineer team driving product innovation, resulting in expanded portfolio scope and successful project acquisitions.}
      \item {Orchestrated 24/7 global support operations across 35+ datacenters, overseeing infrastructure processing 1B+ weekly transactions on 500K machines.}
      \item {\textbf{Distinguished as youngest Product Owner in EVP organization at age 25.}}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Salesforce - Autonomous Infrastructure Control Plane} % Organization
    {San Francisco, CA} % Location
    {Nov. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded VP/SVP-level technical initiatives, architecting enterprise solutions with organization-wide impact.}
        \item {Architected system abstractions to create scalable, reusable products; spearheaded cross-functional adoption across multiple business units.}
        \item {Owned full development process from story creation through deployment, independently developing, delivering, and maintaining production-ready features on schedule.}
        \item {\textbf{Recognized in top 5\% of employees for driving cross-cloud customer initiatives.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Salesforce - Autonomous Infrastructure, Health Pipeline} % Organization
    {San Francisco, CA} % Location
    {Nov. 2020 - Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Rearchitected and developed novel distributed processing system, implementing custom async workflows and auto-scaling mechanisms to scale from 5M to 30M daily requests; achieved 50\% latency reduction while supporting 6x customer growth.}
        \item {Redesigned system architecture for customer data ingestion, scaling report processing from 100K to <1 compute-hour daily (98\% reduction) while achieving 100x collection throughput.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Associate Software Engineer} % Job title
    {Salesforce - Autonomous Infrastructure, Health Pipeline} % Organization
    {San Francisco, CA} % Location
    {July 2019 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected distributed agent system for 300K machines, processing 5M+ daily requests and scaling health pipeline to handle 50M+ daily events.}
        \item {Engineered high-performance data storage architecture, achieving 5x database scalability and 67\% latency reduction through optimized indexing and retrieval patterns while maintaining linear storage complexity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Salesforce - Marketing Cloud, Google Integrations} % Organization
    {Indianapolis, IN} % Location
    {May. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Won the Futureforce Technology Award for outstanding technical talent and aptitude shown during the internship.}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
