%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Philanthropy}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Board of Directors} % Affiliation/role
  {Averroes High School} % Organization/group
  {Fremont, CA} % Location
  {June 2022 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Lead strategic business development initiatives, implementing enterprise solutions including Salesforce CRM and financial management systems, while establishing comprehensive operational frameworks and spearheading fundraising campaigns.}
      \item {Orchestrated comprehensive growth strategy resulting in 25\% increase in freshman enrollment, 100\% growth in donor contributions, and 80\% reduction in administrative overhead through strategic technology adoption.}
      \item {Established data-driven decision-making processes for board operations, implementing quarterly performance metrics and developing sustainable five-year growth strategy for student enrollment and financial sustainability.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {President and Executive Director} % Affiliation/role
    {Ravine Non-Profit Solutions} % Organization/group
    {Santa Clara, CA} % Location
    {Aug. 2020 - Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Founded and scaled pro-bono technology consulting organization to 20+ professionals, providing strategic technical solutions to Bay Area non-profits.}
        \item {Directed comprehensive digital transformation initiatives for 6+ non-profits, encompassing Salesforce implementations, web development, and operational process optimization, resulting in measurable efficiency improvements.}
        \item {Developed structured mentorship program pairing technology professionals with non-profit leaders, facilitating knowledge transfer and sustainable technological independence for partner organizations.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
